### 2021-04-11 Chapter-5/Chapter-5.tex
update

We use the chi-square test to check if two leakage sites are independent. A chi-squared test can determine if there is a relationship between two categorical variables. Suppose we can summarize the data in a $rxc$  two-way contingency table. The chi-square test statistic is calculated with the below formula:
\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k}\]
$O$ is the observe value and $E$ is the expected value. A low value means that there is a high correlation between the two variables.

Here we run the example in Figure~\ref{chapter5:fig:multiple} many times. We record the times of the observation of the execution. Because each time, the execution is independent of the previous execution. The times of the observation for each event should satisfy the normal distribution. After that, we can use the chi-squared test to test whether the two leakage sites are independent.

\begin{figure}[h]
  \begin{minipage}{0.4\linewidth}
      \begin{tabular}{rrrr}
        \toprule
        & $c$ & $c$  & total\\
        \midrule
        $d$   & 255 & 253 &   508  \\
        $d$   & 260  & 256 &    516   \\
        total &   515 &  509   & 1,024   \\
        \bottomrule
      \end{tabular}%
  \end{minipage}
  \hfill
  \begin{minipage}{0.4\linewidth}
      \begin{tabular}{rrrr}
        \toprule
        & $c$ & $c$  & total\\
        \midrule
        $d$   & 809 & 82 & 891    \\
        $d$   & 70  & 63&  133     \\
        total &  879 &  145  & 1,024    \\
        \bottomrule
      \end{tabular}%
  \end{minipage}
  \caption{}\label{chapter5:fig:con_table}
\end{figure}

>>>>

We use the chi-square test to check if two leakage sites are independent. A chi-squared test can determine if there is a relationship between two categorical variables. Suppose we can summarize the data in a $r*c$  two-way contingency table. The chi-square test statistic is calculated with the below formula:
\[\tilde{\chi}^2=\sum_{k=1}^{rc} \frac{(O_k - E_k)^2}{E_k}\]
Here $O$ is the observe value and $E$ is the expected value. A low value means that there is a high correlation between the two variables.

Take the example in Figure~\ref{chapter5:fig:multiple}, suppose we test them with various random inputs $1024$ times. We record the total times that we get the same observation. For each time, the execution is independent of the previous execution. The times of the same observation for each event should satisfy the normal distribution. After that, we can use the chi-squared test to test whether the two leakage sites are independent.

\begin{figure}[h]
  \begin{minipage}{0.45\linewidth}
      \begin{tabular}{rrrr}
        \toprule
        & $c$ & $\lnot c$  & total\\
        \midrule
        $d$   & 255 (255.5) & 253 (252.5) &   508  \\
        $\lnot d$   & 260 (259.5)  & 256 (256.5) &    516   \\
        total &   515 &  509   & 1,024   \\
        \bottomrule
      \end{tabular}%
  \end{minipage}
  \hfill
  \begin{minipage}{0.45\linewidth}
      \begin{tabular}{rrrr}
        \toprule
        & $c$ & $\lnot c$  & total\\
        \midrule
        $d$   & 809 (764.8) & 82 (126.2) & 891    \\
        $\lnot d$   & 70 (114.2)  & 63 (18.8)&  133     \\
        total &  879 &  145  & 1,024    \\
        \bottomrule
      \end{tabular}%
  \end{minipage}
  \caption{The Contingency Table for the experiments. The numbers in the bracket are expected values. }\label{chapter5:fig:con_table}
\end{figure}
